---
title: "Vignette for eatmyshorts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{eatmyshorts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = T
)
```

## Boston Housing example (from `BART` vignette)

First we fit the BART model on two variables (for simplicity). Note that we are only returning 5 trees from the 1000 post-burnin samples, and only using 10 trees in total.

```{r boston}

suppressPackageStartupMessages({
library(eatmyshorts)
library(dplyr)
library(ggplot2)
library(BART)
library(tidytree)
})

Boston <- MASS::Boston

X <- Boston[, c(6, 13)]
y <- Boston$medv

set.seed(99)
bart_model <- wbart(x.train = X, 
                  y.train = y, 
                  nskip = 1000, 
                  ndpost = 1000,
                  nkeeptreedraws = 5, # keep only 5 mcmc iteration sum-of-trees
                  ntree = 10, # use only 10 trees in each iteration (default 200)
                  printevery = 1000
                  ) 

```

The current methods for extracting the trees from the `BART` models are summarise below.

```{r tree-extract}
# Current methods for extracting trees:

tidytree_simple <- as_tidytree(bart_model)

tidytree_simple

tidytree_detailed <- as_tidytree(
  bart_model, 
  extra_cols = c("var", "cut", "leaf_value", "is_leaf")
  )

tidytree_detailed

tidygraph_detailed <- as_tidygraph_list(
  bart_model, 
  extra_cols = c("var", "cut", "leaf_value", "is_leaf"))

tidygraph_detailed[1:2]

```


The `tidytree` method returns a `tbl_tree` (special `tibble`) grouped by MCMC iteration and tree number, whilst the `tidygraph` method returns a list of `tbl_graph` which inherit from the `igraph` structure.

By using the `ggraph` and `tidygraph` package together, we can do some simple plotting.

```{r boston-plot, fig.height=5, fig.width=5, cache = F}

library(ggraph)

  ggraph(tidygraph_detailed[[31]], 'dendrogram') + 
    geom_edge_elbow() + 
    geom_node_label(aes(label = label)) +
    theme_graph()

```

This only plots 1 tree from 1 iteration of the BART MCMC. How do we extend it?

